Thesis Title

### 2022-05-16 chapters/chapter_4.tex
update with working version

\label{tab:chap4_s6}\\
Sample     & Raw Megabases & \% DENV DNA & CDS Assembly & Serotype & Genotype \\

@@

\begin{longtable}{@{}llll@{}}
\caption{Representative sequences of serotype 1 diversity in the Dengue Virus Typing Database.}
\label{tab:chap4_s7}\\
Sample   & ViPR Classification & Origin      & Collection Year \\
EU482591 & DENV-1 V            & USA         & 2006            \\
KU509254 & DENV-1 V            & Venezuela   & 2011            \\
MF004384 & DENV-1 V            & France      & 2014            \\
GU131956 & DENV-1 V            & Mexico      & 2006            \\
AF311956 & DENV-1 V            & Brazil      & 1997            \\
FJ205874 & DENV-1 V            & USA         & 1995            \\
FJ478457 & DENV-1 V            & USA         & 1996            \\
EU482567 & DENV-1 V            & USA         & 1998            \\
DQ285559 & DENV-1 V            & Reunion     & 2004            \\
JN903578 & DENV-1 V            & India       & 2007            \\
KP188548 & DENV-1 V            & Brazil      & 2013            \\
JQ922544 & DENV-1 V            & India       & 1963            \\
KX380796 & DENV-1 V            & Singapore   & 2012            \\
JQ922548 & DENV-1 V            & India       & 2005            \\
KP406801 & DENV-1 V            & South Korea & 2004            \\
DQ285562 & DENV-1 V            & Comoros     & 1993            \\
JQ922546 & DENV-1 V            & India       & 1971            \\
EF457905 & DENV-1 III          & Malaysia    & 1972            \\
AF180818 & DENV-1 II           & Unknown     & Unknown         \\
JQ922547 & DENV-1 II           & Thailand    & 1960            \\
KY496855 & DENV-1 IV           & Taiwan      & 2016            \\
LC128301 & DENV-1 IV           & Philippines & 2016            \\
KX951689 & DENV-1 IV           & Taiwan      & 2004            \\
KC762653 & DENV-1 IV           & Indonesia   & 2008            \\
KU509261 & DENV-1 IV           & Indonesia   & 2010            \\
AB189121 & DENV-1 IV           & Indonesia   & 1998            \\
KC762620 & DENV-1 IV           & Indonesia   & 2007            \\
EU863650 & DENV-1 IV           & Chile       & 2002            \\
AB195673 & DENV-1 IV           & Japan       & 2003            \\
AB204803 & DENV-1 IV           & Japan       & 2004            \\
JF459993 & DENV-1 I            & Myanmar     & 2002            \\
KT827371 & DENV-1 I            & China       & 2014            \\
KX620454 & DENV-1 I            & China       & 2014            \\
FJ639670 & DENV-1 I            & Cambodia    & 2001            \\
KU509250 & DENV-1 I            & Thailand    & 2012            \\
KJ755855 & DENV-1 I            & India       & 2013            \\
GU131678 & DENV-1 I            & Viet Nam    & 2008            \\
KU509265 & DENV-1 I            & Unknown     & 2012            \\
KF955446 & DENV-1 I            & Viet Nam    & 2008            \\
JF937615 & DENV-1 I            & Viet Nam    & 2008            \\
FJ639678 & DENV-1 I            & Cambodia    & 2003            \\
EU660395 & DENV-1 I            & Viet Nam    & 2007            \\
AB608789 & DENV-1 I            & Taiwan      & 1994            \\
GQ868636 & DENV-1 I            & Cambodia    & 2008            \\
KY586539 & DENV-1 I            & Thailand    & 1995            \\
KU509258 & DENV-1 I            & Eritrea     & 2010           
\end{longtable}

@@

\label{tab:chap4_s8}\\
Sample   & ViPR Classification        & Origin       & Collection Year \\

@@

\begin{longtable}{@{}llll@{}}
\caption{Representative sequences of serotype 3 diversity in the Dengue Virus Typing Database.}
\label{tab:chap4_s9}\\
Sample   & ViPR Classification & Origin           & Collection Year \\
KF954946 & DENV-3-III          & China            & 2013            \\
JQ922557 & DENV-3 III          & India            & 2005            \\
KU509286 & DENV-3 III          & India            & 2011            \\
EU687233 & DENV-3 III          & USA              & 2002            \\
GQ252674 & DENV-3 III          & Sri Lanka        & 1997            \\
FJ882573 & DENV-3 III          & Sri Lanka        & 1993            \\
GQ199887 & DENV-3 III          & Sri Lanka        & 1983            \\
JQ922555 & DENV-3 III          & India            & 1966            \\
HM631854 & DENV-3 II           & Cambodia         & 2008            \\
KY586703 & DENV-3 II           & Thailand         & 2006            \\
KU509280 & DENV-3 II           & Thailand         & 2011            \\
FJ744730 & DENV-3 II           & Thailand         & 2001            \\
KY586814 & DENV-3 II           & Thailand         & 2006            \\
DQ863638 & DENV-3 II           & Thailand         & 1973            \\
KC762684 & DENV-3 I            & Indonesia        & 2007            \\
KY863456 & DENV-3 I            & Indonesia        & 2016            \\
KC762691 & DENV-3 I            & Indonesia        & 2008            \\
KC762692 & DENV-3 I            & Indonesia        & 2010            \\
KY794787 & DENV-3 I            & Papua New Guinea & 2007            \\
MF004386 & DENV-3 I            & Malaysia         & 2012            \\
AB189128 & DENV-3 I            & Indonesia        & 1998            \\
KU509279 & DENV-3 I            & Philippines      & 2008            \\
FJ898455 & DENV-3 I            & Cook Islands     & 1991            \\
KU725666 & DENV-3 V            & Unkown           & Unknown        
\end{longtable}

>>>>

\label{tab:chap4_s6}\\ \toprule

@@

\begin{longtable}{@{}llll@{}}
\caption{Representative sequences of serotype 1 diversity in the Dengue Virus Typing Database.}
\label{tab:chap4_s7}\\ \toprule
Sample   & ViPR Classification & Origin      & Collection Year \\ \midrule
EU482591 & DENV-1 V            & USA         & 2006            \\
KU509254 & DENV-1 V            & Venezuela   & 2011            \\
MF004384 & DENV-1 V            & France      & 2014            \\
GU131956 & DENV-1 V            & Mexico      & 2006            \\
AF311956 & DENV-1 V            & Brazil      & 1997            \\
FJ205874 & DENV-1 V            & USA         & 1995            \\
FJ478457 & DENV-1 V            & USA         & 1996            \\
EU482567 & DENV-1 V            & USA         & 1998            \\
DQ285559 & DENV-1 V            & Reunion     & 2004            \\
JN903578 & DENV-1 V            & India       & 2007            \\
KP188548 & DENV-1 V            & Brazil      & 2013            \\
JQ922544 & DENV-1 V            & India       & 1963            \\
KX380796 & DENV-1 V            & Singapore   & 2012            \\
JQ922548 & DENV-1 V            & India       & 2005            \\
KP406801 & DENV-1 V            & South Korea & 2004            \\
DQ285562 & DENV-1 V            & Comoros     & 1993            \\
JQ922546 & DENV-1 V            & India       & 1971            \\
EF457905 & DENV-1 III          & Malaysia    & 1972            \\
AF180818 & DENV-1 II           & Unknown     & Unknown         \\
JQ922547 & DENV-1 II           & Thailand    & 1960            \\
KY496855 & DENV-1 IV           & Taiwan      & 2016            \\
LC128301 & DENV-1 IV           & Philippines & 2016            \\
KX951689 & DENV-1 IV           & Taiwan      & 2004            \\
KC762653 & DENV-1 IV           & Indonesia   & 2008            \\
KU509261 & DENV-1 IV           & Indonesia   & 2010            \\
AB189121 & DENV-1 IV           & Indonesia   & 1998            \\
KC762620 & DENV-1 IV           & Indonesia   & 2007            \\
EU863650 & DENV-1 IV           & Chile       & 2002            \\
AB195673 & DENV-1 IV           & Japan       & 2003            \\
AB204803 & DENV-1 IV           & Japan       & 2004            \\
JF459993 & DENV-1 I            & Myanmar     & 2002            \\
KT827371 & DENV-1 I            & China       & 2014            \\
KX620454 & DENV-1 I            & China       & 2014            \\
FJ639670 & DENV-1 I            & Cambodia    & 2001            \\
KU509250 & DENV-1 I            & Thailand    & 2012            \\
KJ755855 & DENV-1 I            & India       & 2013            \\
GU131678 & DENV-1 I            & Viet Nam    & 2008            \\
KU509265 & DENV-1 I            & Unknown     & 2012            \\
KF955446 & DENV-1 I            & Viet Nam    & 2008            \\
JF937615 & DENV-1 I            & Viet Nam    & 2008            \\
FJ639678 & DENV-1 I            & Cambodia    & 2003            \\
EU660395 & DENV-1 I            & Viet Nam    & 2007            \\
AB608789 & DENV-1 I            & Taiwan      & 1994            \\
GQ868636 & DENV-1 I            & Cambodia    & 2008            \\
KY586539 & DENV-1 I            & Thailand    & 1995            \\
KU509258 & DENV-1 I            & Eritrea     & 2010           
\end{longtable}

@@

\label{tab:chap4_s8}\\ \toprule
Sample   & ViPR Classification        & Origin       & Collection Year \\ \midrule

@@

\begin{longtable}{@{}llll@{}}
\caption{Representative sequences of serotype 3 diversity in the Dengue Virus Typing Database.}
\label{tab:chap4_s9}\\ \toprule
Sample   & ViPR Classification & Origin           & Collection Year \\ \midrule
KF954946 & DENV-3-III          & China            & 2013            \\
JQ922557 & DENV-3 III          & India            & 2005            \\
KU509286 & DENV-3 III          & India            & 2011            \\
EU687233 & DENV-3 III          & USA              & 2002            \\
GQ252674 & DENV-3 III          & Sri Lanka        & 1997            \\
FJ882573 & DENV-3 III          & Sri Lanka        & 1993            \\
GQ199887 & DENV-3 III          & Sri Lanka        & 1983            \\
JQ922555 & DENV-3 III          & India            & 1966            \\
HM631854 & DENV-3 II           & Cambodia         & 2008            \\
KY586703 & DENV-3 II           & Thailand         & 2006            \\
KU509280 & DENV-3 II           & Thailand         & 2011            \\
FJ744730 & DENV-3 II           & Thailand         & 2001            \\
KY586814 & DENV-3 II           & Thailand         & 2006            \\
DQ863638 & DENV-3 II           & Thailand         & 1973            \\
KC762684 & DENV-3 I            & Indonesia        & 2007            \\
KY863456 & DENV-3 I            & Indonesia        & 2016            \\
KC762691 & DENV-3 I            & Indonesia        & 2008            \\
KC762692 & DENV-3 I            & Indonesia        & 2010            \\
KY794787 & DENV-3 I            & Papua New Guinea & 2007            \\
MF004386 & DENV-3 I            & Malaysia         & 2012            \\
AB189128 & DENV-3 I            & Indonesia        & 1998            \\
KU509279 & DENV-3 I            & Philippines      & 2008            \\
FJ898455 & DENV-3 I            & Cook Islands     & 1991            \\
KU725666 & DENV-3 V            & Unkown           & Unknown        
\end{longtable}

### 2022-05-16 chapters/chapter_6.tex
update with working version

hAMRonization

>>>>

C. I. Mendes, F. Maguire, A. Manuele, D. Fornika, S. Tausch, T. Le-Viet, J. Phelan, C. Meehan, A. Raphenya, B. Alcock, E. Culp, A. McArthur, M. Feldgarden, G. Tyson, M. Galas, J. Campos, A. Witney, D. Aanensen, A. Black, L. Katz, P. Oluniyi, I. Olawoye, R. Timme, A. T. Vasconcelos, A. Page, D. MacCannell, E. Griffiths. 
hAMRonization: Enhancing antimicrobial resistance prediction using PHA4GE standards and specification

My contribution to this publication included the development of the antimicrobial detection con-
textual data specification package, including it’s conversion and availability in a machine-
applicable JSON format. It also includes the design and implementation of the hAMRonization package, results analysis, manuscript production and editing.

### 2022-05-16 chapters/chapter_8.tex
update with working version

TO DO

@@

The result of an automated test in the context of one computational workspace does not ensure the same result will be obtained in a different setup. It is important to ensure your software can be installed and used across supported platforms. One way to ensure this is to test on different environments, with varying dependency versions (e.g. multiple Python versions, instead of only the most recent one). Developers can gain increased benefits of testing if tests are run on different setups automatically (see recommendation #4 and Fig. \ref{}).

@@

For prospective users, it is good to know whether you have tested your software and, if so, which tests you have included. This can be done by displaying a badge \cite{trockman_adding_2018} (see \url{https://github.com/microbinfie-hackathon2020/CSIS/blob/main/README.md#example-software-testing}), or linking to your defined testing strategy e.g. a GitHub Actions YAML, (see recommendation \#2, Fig. \ref{}). Documenting the testing goal and process enables end-users to easily check tool functionality and the level of testing \cite{karimzadeh_top_2018}.

@@

>>>>

Computational algorithms have become an essential component of microbiome research, with great efforts by the scientific community to raise standards on the development and distribution of code. Despite these efforts, sustainability and reproducibility are major issues since continued validation through software testing is still not a widely adopted practice.

In the field of microbial bioinformatics, good software engineering practices are not yet widely adopted. Many microbial bioinformaticians start out as (micro)biologists and subsequently learn how to code. Without abundant formal training, a lot of education about good software engineering practices comes down to an exchange of information within the microbial bioinformatics community.

Here, we report seven recommendations that help researchers implement software testing in microbial bioinformatics. These recommendations are: Establish software needs and testing goals; Use appropriate input test files; Use an easy-to-follow language format to implement testing; Try to automate testing; Test across multiple computational setups; and Encourage others to test your software.

We propose collaborative software testing as an opportunity to continuously engage software users, developers, and students to unify scientific work across domains. As automated software testing remains underused in scientific software, our set of recommendations not only ensures appropriate effort can be invested into producing high quality and robust software but also increases engagement in its sustainability.

We have developed these recommendations based on our experience from a collaborative hackathon organised prior to the American Society for Microbiology Next Generation Sequencing (ASM NGS) 2020 conference. We also present a repository hosting examples and guidelines for testing, available from \url{https://github.com/microbinfie-hackathon2020/CSIS}.

My contribution to this publication included the development of the seven recommendations here presented, including examples of software testing. Additionally, I have also contributed to the manuscript production and
editing.

@@

The result of an automated test in the context of one computational workspace does not ensure the same result will be obtained in a different setup. It is important to ensure your software can be installed and used across supported platforms. One way to ensure this is to test on different environments, with varying dependency versions (e.g. multiple Python versions, instead of only the most recent one). Developers can gain increased benefits of testing if tests are run on different setups automatically (see recommendation \#4 and Fig. \ref{tab:ch8_table_sup1}).

@@

For prospective users, it is good to know whether you have tested your software and, if so, which tests you have included. This can be done by displaying a badge \cite{trockman_adding_2018} (see \url{https://github.com/microbinfie-hackathon2020/CSIS/blob/main/README.md#example-software-testing}), or linking to your defined testing strategy e.g. a GitHub Actions YAML, (see recommendation \#2, Fig. \ref{tab:ch8_table_sup1}). Documenting the testing goal and process enables end-users to easily check tool functionality and the level of testing \cite{karimzadeh_top_2018}.

@@

\begin{figure*}[]
\centering
\includegraphics[width=\textwidth]{figures/chapter 8/sup_fig_1.png}
\caption{Example YAML file for a GitHub Actions workflow.}
\label{fig:chap8_sup_figure1}
\end{figure*}

\begin{table}[]
\centering
\caption{Software tested during the ASM NGS 2020 hackathon}
\label{tab:ch8_table_sup1}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}llll@{}}
\toprule
Software Name &
  Software (URL) &
  Test File (URL) &
  Literature Citation (DOI) \\ \midrule
BUSCO &
  \begin{tabular}[c]{@{}l@{}}https://gitlab.com/\\ ezlab/busco\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/busco.yml\end{tabular} &
  10.1093/bioinformatics/btv351 \\
Centrifuge &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ DaehwanKimLab/centrifuge\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/centrifuge.yml\end{tabular} &
  10.1101/gr.210641.116 \\
CheckM &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ Ecogenomics/CheckM\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/checkm.yml\end{tabular} &
  10.1101/gr.186072.114 \\
chewBBACA &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ B-UMMI/chewBBACA\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/B-UMMI/\\ chewBBACA/blob/master/\\ .github/workflows/chewbbaca.yml\end{tabular} &
  10.1099/mgen.0.000166 \\
CSIS &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ microbinfie-hackathon2020/CSIS\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/CSIS.yml\end{tabular} &
  this manuscript \\
Genotyphi &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ katholt/genotyphi\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/genotyphi.yml\end{tabular} &
  10.1038/ncomms12827 \\
Kraken &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ DerrickWood/kraken\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/kraken.yml\end{tabular} &
  10.1186/gb-2014-15-3-r46 \\
Kraken2 &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ DerrickWood/kraken2\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/kraken2.yml\end{tabular} &
  10.1186/s13059-019-1891-0 \\
KrakenUniq &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ fbreitwieser/krakenuniq\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/krakenuniq.yml\end{tabular} &
  10.1186/s13059-018-1568-0 \\
Pangolin &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ cov-lineages/pangolin\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/pangolin.yml\end{tabular} &
  absent \\
Prokka &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ tseeman/prokka\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/prokka.yml\end{tabular} &
  10.1093/bioinformatics/btu153 \\
Quast &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ ablab/quast\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/quast.yml\end{tabular} &
  10.1093/bioinformatics/btt086 \\
Shovill &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ tseemann/shovill\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/shovill.yml\end{tabular} &
  absent \\
SKESA &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ ncbi/SKESA\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/skesa.yml\end{tabular} &
  10.1186/s13059-018-1540-z \\
Trycycler &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ rrwick/Trycycler\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/trycycler.yml\end{tabular} &
  10.5281/zenodo.4430941 \\
Unicycler &
  \begin{tabular}[c]{@{}l@{}}https://github.com/\\ rrwick/Unicycler\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}https://github.com/microbinfie-\\ hackathon2020/CSIS/blob/main/\\ .github/workflows/unicycler.yml\end{tabular} &
  10.1371/journal.pcbi.1005595 \\ \bottomrule
\end{tabular}%
}
\end{table}
